% Telekom osCompendium extract template
%
% (c) Karsten Reincke, Deutsche Telekom AG, Darmstadt 2011
%
% This LaTeX-File is licensed under the Creative Commons Attribution-ShareAlike
% 3.0 Germany License (http://creativecommons.org/licenses/by-sa/3.0/de/): Feel
% free 'to share (to copy, distribute and transmit)' or 'to remix (to adapt)'
% it, if you '... distribute the resulting work under the same or similar
% license to this one' and if you respect how 'you must attribute the work in
% the manner specified by the author ...':
%
% In an internet based reuse please link the reused parts to www.telekom.com and
% mention the original authors and Deutsche Telekom AG in a suitable manner. In
% a paper-like reuse please insert a short hint to www.telekom.com and to the
% original authors and Deutsche Telekom AG into your preface. For normal
% quotations please use the scientific standard to cite.
%
% [ File structure derived from 'mind your Scholar Research Framework' 
%   mycsrf (c) K. Reincke CC BY 3.0  http://mycsrf.fodina.de/ ]

%
% select the document class
% S.26: [ 10pt|11pt|12pt onecolumn|twocolumn oneside|twoside notitlepage|titlepage final|draft
%         leqno fleqn openbib a4paper|a5paper|b5paper|letterpaper|legalpaper|executivepaper openrigth ]
% S.25: { article|report|book|letter ... }
%
% oder koma-skript S.10 + 16
\documentclass[DIV=calc,BCOR=5mm,11pt,headings=small,oneside,abstract=true, toc=bib]{scrartcl}

%%% (1) general configurations %%%
\usepackage[utf8]{inputenc}

%%% (2) language specific configurations %%%
\usepackage[]{a4,ngerman}
\usepackage[english, german, ngerman]{babel}
\selectlanguage{ngerman}

%language specific quoting signs
%default for language emglish is american style of quotes
\usepackage{csquotes}

% jurabib configuration
\usepackage[see]{jurabib}
\bibliographystyle{jurabib}
\input{../btexmat/oscJbibCfgDeInc}

% language specific hyphenation
\input{../btexmat/oscHyphenationDeInc}

%%% (3) layout page configuration %%%

% select the visible parts of a page
% S.31: { plain|empty|headings|myheadings }
%\pagestyle{myheadings}
\pagestyle{headings}

% select the wished style of page-numbering
% S.32: { arabic,roman,Roman,alph,Alph }
\pagenumbering{arabic}
\setcounter{page}{1}

% select the wished distances using the general setlength order:
% S.34 { baselineskip| parskip | parindent }
% - general no indent for paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.2ex plus 0.2ex minus 0.2ex}


%%% (4) general package activation %%%
%\usepackage{utopia}
%\usepackage{courier}
%\usepackage{avant}
\usepackage[dvips]{epsfig}

% graphic
\usepackage{graphicx,color}
\usepackage{array}
\usepackage{shadow}
\usepackage{fancybox}

%- start(footnote-configuration)
%  flush the cite numbers out of the vertical line and let
%  the footnote text directly start in the left vertical line
\usepackage[marginal]{footmisc}
%- end(footnote-configuration)

\begin{document}

%% use all entries of the bliography

%%-- start(titlepage)
\titlehead{Literaturexzerpt}
\subject{Autor(en): \ldots}
\title{Titel: \ldots}
\subtitle{Jahr: \ldots }
\author{K. Reincke\input{../btexmat/oscLicenseFootnoteInc}}

%\thanks{den Autoren von KOMA-Script und denen von Jurabib}
\maketitle
%%-- end(titlepage)
%\nocite{*}

\section{abstracts}
\subsection{1. Aufl. 2002}
Das Werk / The work\footcite[][]{JaeMet2002a}:

\textbf{DE:} Die 1. Ausgabe des wichtigsten deutschsprachigen Standardwerks zum Thema
'Open Source Lizenzen'; es behandelt wichtige Aspekte wie Haftung, Patente oder
Marken. Und bzgl. jeder aufgelisteten Lizenz oder jedes erwähnten Lizenzclusters
beschreibt es Rechte und Pflichten der Softwarenutzer - nur leider eben nicht in
Form abarbeitbarer Listen und auch nicht unter Berücksichtigung der
verschiedenen Usecases, wie sie die Softwareentwicklung kennzeichnen. Und
trotzdem: es ist ein unumgehbares Standardwerk, zumindest in seiner letzten
Ausgabe von 2011.

\textbf{EN:} This is the first edition of the most important German standard work
concerning Open Source Software Licenses. It deals with many important topics
like liability, patents, or branding, And with respect to each of the mentioned
licenses (or license clusters) it discusses already the rights and the duties of
the software user - but regrettably not in form of a processable todo-list and
not with distinguishing the different use cases of the software development
process. But nevertheless: it's a very important groundwork!

\subsection{2. Aufl. 2006}
Das Werk / The work\footcite[][]{JaeMet2006a} \\

\textbf{DE:}  Die 2. Ausgabe des wichtigsten deutschsprachigen Standardwerks zum
Thema 'Open Source Lizenzen': Wie ifross unterteilt es Lizenzen jetzt als solche
mit 'strenger Copyleft Klausel', solche mit 'beschränkter Copyleft-Klausel' und
solche ohne 'Copyleft-Klausel'. Neben anderen Aspekten diskutiert das Buch nun
die Durchsetzung von Open Source Lizenzen und die Wechselwirkungen zum AGB
Recht. Und erneut beschreibt es bzgl. der wichtigsten Open Source Lizenzen
Rechte und Pflichten der Softwarenutzer - wiederum nur leider eben nicht in Form
abarbeitbarer Listen und auch nicht unter Berücksichtigung der verschiedenen
Usecases, wie sie die Softwareentwicklung kennzeichnen. Allerdings bleibt es
natürlich ein unumgehbares Standardwerk!

\textbf{EN:} This is the second strongly expanded edition of the most important
German standard work concerning Open Source Software Licenses. Like ifross it
classifies licenses as those with 'strict copyleft clauses', those with
'restricted copyleft-clauses' and those without any 'copyleft-clauses'. Beside
other aspects it now discusses how to achieve acceptance of an Open Source
licensing and analyzes the AGB side effects. And again it discusses the rights
and the duties of the software user, at least with respect to the most import
Open Source Licenses - but again regrettably not in form of a processable
todo-list and not with distinguishing the different use cases of the software
development process. But naturally: it remains a very important groundwork!

\subsection{3. Aufl. 2011}
Das Werk / The work\footcite[][]{JaeMet2011a} \\

\textbf{DE:} Die 3. aktuelle Ausgabe des wichtigsten deutschsprachigen
Standardwerks zum Thema 'Open Source Lizenzen': Behält die 'bewährte
Kapitelstruktur' bei, listet aber neue Lizenzenh auf und nebst vielem anderem
auvh auf die Lizenzkombination ein. Ergo findet man erneut zu Open Source
Lizenzen die Rechte und Pflichten der Softwarenutzer - wiederum nur leider eben
nicht in Form abarbeitbarer Listen und auch nicht unter Berücksichtigung der
verschiedenen Usecases, wie sie die Softwareentwicklung kennzeichnen. Das
scheidet der Qualität dieses unumgehbaren Standardwerks nicht!

\textbf{EN:} This is the third current edition of the most important German
standard work concerning Open Source Software Licenses. It retains the
'established structure of the chapters', adds new licenses and discusses -
beside many other aspects - the compatibility respectively combinability of
different licenses. Hence this work again specifies the rights and the duties of
the software user, at least with respect to the most important licenses - but
again regrettably not in form of a processable todo-list and not with
distinguishing the different use cases of the software development process. But
it retains the most important groundwork!

\subsection{Unterschied in der Klassifikation}

Während die erste Auflage noch bipolar die Rechte und Pflichten
der Nutzer von \enquote{'Copyleft'-Lizenzen} denen der Nutzer von
\enquote{'BSD'-artigen Lizenzen gegenüberstellt} wobei LGPL und GPL unter
den Copyleft-Lizenzehn subsumiert werden, wechsel die zweite Auflage zur
Klassifikation von ifross: Hier ist die Rede von 

\section{Line of Thought}

\section{Specific Aspects}

\small
\bibliography{../bibfiles/oscResourcesDe}

\end{document}
