% Telekom osCompendium extract template
%
% (c) Karsten Reincke, Deutsche Telekom AG, Darmstadt 2011
%
% This LaTeX-File is licensed under the Creative Commons Attribution-ShareAlike
% 3.0 Germany License (http://creativecommons.org/licenses/by-sa/3.0/de/): Feel
% free 'to share (to copy, distribute and transmit)' or 'to remix (to adapt)'
% it, if you '... distribute the resulting work under the same or similar
% license to this one' and if you respect how 'you must attribute the work in
% the manner specified by the author ...':
%
% In an internet based reuse please link the reused parts to www.telekom.com and
% mention the original authors and Deutsche Telekom AG in a suitable manner. In
% a paper-like reuse please insert a short hint to www.telekom.com and to the
% original authors and Deutsche Telekom AG into your preface. For normal
% quotations please use the scientific standard to cite.
%
% [ File structure derived from 'mind your Scholar Research Framework' 
%   mycsrf (c) K. Reincke CC BY 3.0  http://mycsrf.fodina.de/ ]

%
% select the document class
% S.26: [ 10pt|11pt|12pt onecolumn|twocolumn oneside|twoside notitlepage|titlepage final|draft
%         leqno fleqn openbib a4paper|a5paper|b5paper|letterpaper|legalpaper|executivepaper openrigth ]
% S.25: { article|report|book|letter ... }
%
% oder koma-skript S.10 + 16
\documentclass[DIV=calc,BCOR=5mm,11pt,headings=small,oneside,abstract=true, toc=bib]{scrartcl}

%%% (1) general configurations %%%
\usepackage[utf8]{inputenc}

%%% (2) language specific configurations %%%
\usepackage[]{a4,ngerman}
\usepackage[ngerman, german, english]{babel}
\selectlanguage{english}

%language specific quoting signs
%default for language emglish is american style of quotes
\usepackage{csquotes}

% jurabib configuration
\usepackage[see]{jurabib}
\bibliographystyle{jurabib}
\input{../btexmat/oscJbibCfgEnInc}

% language specific hyphenation
\input{../btexmat/oscHyphenationEnInc}

%%% (3) layout page configuration %%%

% select the visible parts of a page
% S.31: { plain|empty|headings|myheadings }
%\pagestyle{myheadings}
\pagestyle{headings}

% select the wished style of page-numbering
% S.32: { arabic,roman,Roman,alph,Alph }
\pagenumbering{arabic}
\setcounter{page}{1}

% select the wished distances using the general setlength order:
% S.34 { baselineskip| parskip | parindent }
% - general no indent for paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.2ex plus 0.2ex minus 0.2ex}


%%% (4) general package activation %%%
%\usepackage{utopia}
%\usepackage{courier}
%\usepackage{avant}
\usepackage[dvips]{epsfig}

% graphic
\usepackage{graphicx,color}
\usepackage{array}
\usepackage{shadow}
\usepackage{fancybox}

%- start(footnote-configuration)
%  flush the cite numbers out of the vertical line and let
%  the footnote text directly start in the left vertical line
\usepackage[marginal]{footmisc}
%- end(footnote-configuration)

\begin{document}

%% use all entries of the bliography

%%-- start(titlepage)
\titlehead{Literaturexzerpt}
\subject{Autor(en): Stallman / Stallman2002b}
\title{Titel: Can You Trust Your Computer}
\subtitle{Jahr: 2002 / 2002 }
\author{K. Reincke\input{../btexmat/oscLicenseFootnoteInc}}

%\thanks{den Autoren von KOMA-Script und denen von Jurabib}
\maketitle
%%-- end(titlepage)
%\nocite{*}

\begin{abstract}
\noindent
\cite[(in:)][]{StaGay2002a} \\
\noindent
\cite[(ist:)][]{Stallman2002b} \\
Das Werk / The work\footcite[][]{Stallman2002b} \\
\noindent \itshape
\ldots Erläutert die Umsetzung von 'DRM' und 'trusted computing' als eine
Verschlüsselung von Daten, die werksseitig immer schon in Software und Computer
eingebaut sei. Da aber in diesem Fall der Schlüssel dem Besitzer vorenthalten
werde, kontrolliere letztlich das Programm respektive die Maschine den Besitzer,
nicht der Besitzer seine Maschine. Und eben deshalb spricht RMS vom 'Digitial
Restriction Management' und vom 'Treacherous Computing'.
\\
\noindent
\ldots The article argues that 'DRM' - realized by a 'trusted computing'
campaign - is technically established by a key based digital encryption of your
data. This encryption is automatically incorporated into your computer
(software). But because the keys are kept secret from the owner of the machine
one can say that the programs using the hidden keys are controlling the owner,
not the owner the computer. Therefore RMS uses the terms 'Digitial Restriction
Management' and 'Treacherous Computing'.
\end{abstract}
\footnotesize
%\tableofcontents
\normalsize

\section{Line of Thought}

The article argues that 'DRM' - realized by a 'trusted computing' campaign - is
technically established by a key based digital encryption of your data. This
encryption is automatically incorporated into your computer (software). But
because the keys are kept secret from the owner of the machine one can say that
the programs using the hidden keys are controlling the owner, not the owner the
computer. Therefore RMS uses the terms ``Digitial Restriction Management'' and
``Treacherous Computing''.\footcite[cf][115]{Stallman2002b}
\section{Specific Aspects}

\small
\bibliography{../bibfiles/oscResourcesEn}

\end{document}
