% Telekom osCompendium extract template
%
% (c) Karsten Reincke, Deutsche Telekom AG, Darmstadt 2011
%
% This LaTeX-File is licensed under the Creative Commons Attribution-ShareAlike
% 3.0 Germany License (http://creativecommons.org/licenses/by-sa/3.0/de/): Feel
% free 'to share (to copy, distribute and transmit)' or 'to remix (to adapt)'
% it, if you '... distribute the resulting work under the same or similar
% license to this one' and if you respect how 'you must attribute the work in
% the manner specified by the author ...':
%
% In an internet based reuse please link the reused parts to www.telekom.com and
% mention the original authors and Deutsche Telekom AG in a suitable manner. In
% a paper-like reuse please insert a short hint to www.telekom.com and to the
% original authors and Deutsche Telekom AG into your preface. For normal
% quotations please use the scientific standard to cite.
%
% [ File structure derived from 'mind your Scholar Research Framework' 
%   mycsrf (c) K. Reincke CC BY 3.0  http://mycsrf.fodina.de/ ]

%
% select the document class
% S.26: [ 10pt|11pt|12pt onecolumn|twocolumn oneside|twoside notitlepage|titlepage final|draft
%         leqno fleqn openbib a4paper|a5paper|b5paper|letterpaper|legalpaper|executivepaper openrigth ]
% S.25: { article|report|book|letter ... }
%
% oder koma-skript S.10 + 16
\documentclass[DIV=calc,BCOR=5mm,11pt,headings=small,oneside,abstract=true, toc=bib]{scrartcl}

%%% (1) general configurations %%%
\usepackage[utf8]{inputenc}

%%% (2) language specific configurations %%%
\usepackage[]{a4,ngerman}
\usepackage[ngerman, german, english]{babel}
\selectlanguage{english}

%language specific quoting signs
%default for language emglish is american style of quotes
\usepackage{csquotes}

% jurabib configuration
\usepackage[see]{jurabib}
\bibliographystyle{jurabib}
\input{../btexmat/oscJbibCfgEnInc}

% language specific hyphenation
\input{../btexmat/oscHyphenationEnInc}

%%% (3) layout page configuration %%%

% select the visible parts of a page
% S.31: { plain|empty|headings|myheadings }
%\pagestyle{myheadings}
\pagestyle{headings}

% select the wished style of page-numbering
% S.32: { arabic,roman,Roman,alph,Alph }
\pagenumbering{arabic}
\setcounter{page}{1}

% select the wished distances using the general setlength order:
% S.34 { baselineskip| parskip | parindent }
% - general no indent for paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.2ex plus 0.2ex minus 0.2ex}


%%% (4) general package activation %%%
%\usepackage{utopia}
%\usepackage{courier}
%\usepackage{avant}
\usepackage[dvips]{epsfig}

% graphic
\usepackage{graphicx,color}
\usepackage{array}
\usepackage{shadow}
\usepackage{fancybox}

%- start(footnote-configuration)
%  flush the cite numbers out of the vertical line and let
%  the footnote text directly start in the left vertical line
\usepackage[marginal]{footmisc}
%- end(footnote-configuration)

\begin{document}

%% use all entries of the bliography

%%-- start(titlepage)
\titlehead{Literaturexzerpt}
\subject{Autor(en): Stallman / Stallman1996b}
\title{Titel: Selling Free Software}
\subtitle{Jahr: 1996 / 2002 }
\author{K. Reincke\input{../btexmat/oscLicenseFootnoteInc}}

%\thanks{den Autoren von KOMA-Script und denen von Jurabib}
\maketitle
%%-- end(titlepage)
%\nocite{*}

\begin{abstract}
\noindent
\cite[(in:)][]{StaGay2002a} \\
\noindent
\cite[(ist:)][]{Stallman1996b} \\
Das Werk / The work\footcite[][]{Stallman1996b} \\
\noindent \itshape
\ldots  
\\ Opponiert gegen den Mythos, dass mit freier Software kein Geld verdient
werden dürfe. Vielmehr lege die GPL diesbzgl. gerade nicht fest, wieviel für das
Kopieren der GNU Software verlangt werden dürfe: das könne kostenlos sein oder
Cents, ein Euro oder Milliraden von Euros kosten.
\noindent
\ldots This article opposes the myth that you should not charge money for
distributing copies of free software. It underlines that - with one exception -
the GPL has no requirements about how much you can charge for distributing a
copy of free software: Following the GPL you can charge nothing, a penny, a
dollar, or a billion dollars.
\end{abstract}
\footnotesize
%\tableofcontents
\normalsize

\section{You are allowed to earn money}
This article opposes the myth that you should not charge money for
distributing copies of free software. 

At the beginning RMS mentions that \enquote{many people believe that the
spirit of the GNU project is that you should not charge money for
distributing copies of software, or that you should charge as little as
possible - just enogh to cover the cost.}\footcite[cf][63]{Stallman1996b}

But RMS also gives a clear answer:

\begin{quote}
\enquote{Since free software is not a matter of price, a low price isn't more
free, or closer to free. So if you are redistributing copies of free software,
you might as well charge a substantial fee and make some money.
}\footcite[cf][63]{Stallman1996b}
\end{quote}

RMS underlines finally that - with one exception - the GPL has no requirements
about how much you can charge for distributing a copy of free software: Following the GPL
you can \enquote{[\ldots] charge nothing, a penny, a dollar, or a billion
dollars}\footcite[cf][64]{Stallman1996b}.

\subsection{The Limit of Earning Money}

Main idea of the GPL is that anything can be organized as any business wants to
do except the act of licensing itself: If you give anyone an application it must
get the source code and the rights of free software too.

But there is one construction inside of the GPL where one has to say something
about the money: it's \enquote{[\ldots] the case where binaries are
distributed without the corresponding complete source
code}\footcite[cf][65]{Stallman1996b}: 

\begin{quote}
\enquote{Without a limit on the fee for the source code, they would be able set a
fee too large for anyone to pay [\ldots] and thus pretend to release source code
while in truth concealing it. So in this case we have to limit the fee for
source, to ensure the user's freedom
}\footcite[][65]{Stallman1996b}.
\end{quote}


\section{\ldots but there's an inherent move to low costs}

RMS also mentions, that \enquote{[\ldots] free software naturally tends to
spread around, and [that] there are many ways to get
it}\footcite[cf][63]{Stallman1996b}. Consequently there is a competition
which levels the price of getting copies to the real costs of copying the
software. [Hence the big money is the service]



\small
\bibliography{../bibfiles/oscResourcesEn}

\end{document}
