% Telekom osCompendium 'for being included' snippet template
%
% (c) Karsten Reincke, Deutsche Telekom AG, Darmstadt 2011
%
% This LaTeX-File is licensed under the Creative Commons Attribution-ShareAlike
% 3.0 Germany License (http://creativecommons.org/licenses/by-sa/3.0/de/): Feel
% free 'to share (to copy, distribute and transmit)' or 'to remix (to adapt)'
% it, if you '... distribute the resulting work under the same or similar
% license to this one' and if you respect how 'you must attribute the work in
% the manner specified by the author ...':
%
% In an internet based reuse please link the reused parts to www.telekom.com and
% mention the original authors and Deutsche Telekom AG in a suitable manner. In
% a paper-like reuse please insert a short hint to www.telekom.com and to the
% original authors and Deutsche Telekom AG into your preface. For normal
% quotations please use the scientific standard to cite.
%
% [ Framework derived from 'mind your Scholar Research Framework' 
%   mycsrf (c) K. Reincke 2012 CC BY 3.0  http://mycsrf.fodina.de/ ]
%


%% use all entries of the bibliography
%\nocite{*}

Grouping Open Source licenses is often used. Even the set of \emph{Open Source
Li\-cen\-ses}\footcite[cf.][\nopage wp]{OSI2012b} itself is already a cluster
which is established by a set of grouping criteria: The \enquote{distribution
terms} of each software license which wants to be an Open Source License,
\enquote{[\ldots] must comply with the [\ldots] criteria} of the \emph{Open
Source Definition}\footcite[cf.][\nopage wp]{OSI2012a}, maintained by the
\emph{Open Source Initiative}\footcite[cf.][\nopage wp]{OSI2012c} and often
abbreviated as \emph{OSD}\footnote{For stating it more precisely: to meet the
OSD, is only a necessary condition for being an Open Source License. The
sufficient condition for becoming an Open Source license, is the approval by the
OSI, which offers a process for becoming an officially approved Open Source
License (\cite[cf.][\nopage wp.]{OSI2012d}).}. This \emph{OSD} demarcates 'the
group of Open Source Licenses' against 'the group of not Open Sources Licenses'.

Another way to cluster the \emph{Free Software Licenses} is specified by the
\enquote{Free Software Definition}. This \emph{FSD} contains four conditions
which must be met by any free software license: it must asign the \enquote{the
freedom to run a program, for any purpose [\ldots]}, \enquote{the freedom to
study how it works, and adapt it to your needs [\ldots]}, \enquote{the freedom
to redistribute copies [\ldots]}, and finally \enquote{the freedom to improve
the program, and release your improvements
[\ldots]}\footcite[cf.][41]{Stallman1996a}. Although sometimes seen as a little
surprise, this way to think leeds directly to the position, that being openly
accessable software is 'only' a derived condition. If the
\enquote{freedom to make changes and the freedom to publish improved versions}
shall be \enquote{meaningful}, then the \enquote{access to the source code of
the program} is a prerequisite. \enquote{Therefore, accessibility of source code
is a necessary condition for free software.}\footcite[cf.][41]{Stallman1996a}

The difference between these two positions is often described as a difference of
emphasizing: Although both definitions \enquote{[\ldots] covers almost exactly
the same range of software}, the \emph{Free Software Foundation} - as it is said
- \enquote{prefers [\ldots] (to emphazise) the idea of freedom [\ldots]} while
the \emph{OSI} wants to underline the philosophically indifferent
\enquote{development methodolgy}\footcite[pars pro toto: cf.][232]{Fogel2006a}.

A third method to establish a special group of free software and free licenses
is specified by the \enquote{Debian Free Software Guideline}, which is embedded
into the \enquote{Debian Social Contract}. This \enquote{DFSG} contains nine
defining criteria which - as Debian itself says - have been \enquote{[\ldots]
adopted by the free[sic!] software community as the basis of the Open Source
Definition}\footcite[cf.][wp]{DFSG2013a}.

A rough understanding of these methods might lead to the conclusion that all
these three definitions are extensionally equal and only differ only
intensionally. But is this true? Le us compare the clusters \emph{OSI approved
licenses}, \emph{OSD compliant Licenses}, \emph{DFSG compliant Licenses}, and
\emph{FSD compliant licenses} extensionally, one has to ask, whether they could
establish different sets of licenses:

Firstly, the most easily to determine difference is established that of
unidirectional an inclusion: By definition, the \emph{OSI approved licenses} and
the \emph{OSD compliant } meet the requirements of the OSD\footcite[cf.][\nopage
wp]{OSI2012a}. But only the \emph{OSI approved licenses} have successfully
passed the OSI process\footcite[cf.][wp]{OSI2012a} and are therefore officially
listed as an Open Source License\footcite[cf.][\nopage wp]{OSI2012b}. So, one
can say, that all \emph{OSI approved licenses} are also OSD fulfilling licenses,
but not vice versa.

Secondly, a similar argumentation leeds to the differences between the
\emph{DFSG compliant licenses} and the \emph{OSI approved licenses}. As it it
stated, the OSD \enquote{[\ldots] is based on the Debian Free Software
Guildeline and any license that meets one definition almost meets the
other}\footcite[cf.][233]{Fogel2006a}. But again, meeting the definition is not
enough for being an official Open Source License: the license has to be approved
by the OSI\footcite[cf.][\nopage wp]{OSI2012b}. So, one can analogically say,
that all \emph{OSI approved licenses} are also \emph{DFSG compliant licenses},
but not vice versa.

Thirdly - with a little generosity by ignoring the \enquote{few exceptions},
which have been appeared \enquote{over the years}\footcite[cf.][233]{Fogel2006a}
- one can say that, because of their kinsmanlike relation, at least the \emph{OSD
fulfilling licenses} are also \emph{DFSG compliant licenses} and vice versa.

Last but not least one has to state, that the (potential) set of free software
licenses must be greater than all the other three sets: On the one side, the FSD
only requires that the license of a software must allow to read and to use the
software, to modify and to distribute it\footcite[cf.][41]{Stallman1996a}. These
conditions are covered by the first three paragraphs of the OSD concerning the
topics \enquote{Free Redistribution}, \enquote{Source Code}, and
\enquote{Derived Works}\footcite[cf.][\nopage wp]{OSI2012a}. On the other side,
the OSD contains seven additional requirements\footnote{For example, see the
condition that \enquote{the license must be technology-neutral}
(\cite[cf.][\nopage wp]{OSI2012a}). Here, one has to consider, that we are
discussing the potentials of the definitions, not the meaning of concrete
licenses. So, in this context, it is irrelevant, that in reality all existing
Free Software Licenses like GPL, LGPL or AGPL indeed are also classfied as Open
Source Licenses. Here, we are referring to the fact, that there might exist (be
generated) licenses which fulfill the FSD, but not the OSD.}, which must be met
by a license for being an OSD compliant license. Hence, logically regarded,
there might exist licenses, which fulfill all conditions of the FSD and
nevertheless do not fulfill at least some conditions of the OSD. So, the
set of all (potential) \emph{Free Software Licenses} must be greater than the
set of all (potential) \emph{Open Source Licenses} and greater than the set of
\emph{OSD compliant licenses}.

So, if we want to sketch the relation of the clusters of the software licenses,
we have to paint the following picture:

\begin{center}

\begin{tikzpicture}
\label{LICTAX}
\small

\node[circle,draw,text width=7cm,fill=gray!10] (l0400) at (5,5)
{  };

\draw [-,dotted,line width=0pt,white,
    decoration={text along path,
              text align={center},
              text={|\itshape \tiny| All Software Licenses}},
              postaction={decorate}] (1.9,5) arc (180:0:3.1cm);

\node[circle,draw,text width=5.4cm, fill=gray!20] (l0300) at (5,5)
{ };

\draw [-,dotted,line width=0pt,white,
    decoration={text along path,
              text align={center},
              text={|\itshape|FSD Compliant Licenses}},
              postaction={decorate}] (2.8,5) arc (180:0:2.25cm);


\node[circle,draw,text width=3.8cm, fill=gray!30] (l0200) at (5,5)
{  };



\draw [-,dotted,line width=0pt,white,
    decoration={text along path,
              text align={center},
              text={|\itshape|DFSG Compliant Licenses}},
              postaction={decorate}] (3.4,5) arc (180:360:1.65cm);

\draw [-,dotted,line width=0pt,white,
    decoration={text along path,
              text align={center},
              text={|\itshape|OSD Compliant Licenses}},
              postaction={decorate}] (3.6,5) arc (180:0:1.45cm);
          
 % (1.A) list of all licenses and their release numbers Level 5/6
\node[circle,draw,text width=1.6cm, fill=gray!40, text centered] (l0100) at (5,5)
{ \bfseries \textit{OSI} \\ \textit{approved} \\ \textit{Licenses} };
\end{tikzpicture}
\end{center}

It should be clear without longer explanations, that these clusters don't allow
to conclude to a correct behaviour according to the Open Source Licenses: On the
one hand, all larger clusters do not talk about the Open Source Licenses. On the
other hand the Open Source License cluster only collects his elements on the
base of the OSD which do not stipulates a concrete license fulfilling actions
of the licensee.

The next level of clusteringing Open Source Licenses concerns the inner
structure of the OSI approved licenses. Even the OSI has recently discussed
whether a better kind of grouping the listed licenses would better fit the needs
of the visitors of the OSI site\footcite[cf.][\nopage wp]{OSI2013a}. And finally
the OSI ends up in the categories \enquote{popular and widely used (licenses) or
with strong communities}, \enquote{special purpose licenses},
\enquote{other/Miscellaneous licenses}, \enquote{licenses that are redundant
with more popular licenses}, \enquote{non-reusable licenses},\enquote{Superseded
licenses}, \enquote{Licenses that have been voluntarily retired}, and \enquote{
Uncategorized Licenses}\footcite[cf.][\nopage wp]{OSI2013b}.

Another way to structure the field of Open Source Licenses is to think in
\enquote{types of Open Source Licenses} by grouping the \enquote{\emph{Academic
licenses}, so named because they were originally created by academic
institutions}\footcite[cf.][69]{Rosen2005a}, the \enquote{\emph{Reciprocal
licenses}}, so named because they \enquote{[\ldots] require the distributors of
derivative works to distribute those works under same license including the
requirement that the source code of those derivative qorks be
published}\footcite[cf.][70]{Rosen2005a}, the \enquote{\emph{Standard
licenses}}, so named because the refer to the reusability of \enquote{industry
standards}\footcite[cf.][70]{Rosen2005a}, and the \enquote{\emph{Content
licenses}}, so named because they refer to
\enquote{[\ldots] other than software, such as music art, film, literary works}
and so on\footcite[cf.][71]{Rosen2005a}.

Although these specifications directly help to find the relevant licenses which
should be used for new (software) projects, none of these categories does allow
to infer the license compliant behaviour, because the categories are mostly
defined on the base of license external criteria: whether a license is published
by a specific kind of organizations or whether license concerns industry
standards or other kind of works than software, is not a question of the license
fulfilling behaviour.

Only the grouping into the \enquote{\emph{academic licenses}} and the
\enquote{\emph{reciprocal licenses}} touches the idea of license fulfilling
doings, if one expands the definition of the \enquote{\emph{Academic licenses}}
by the specification, that these licenses \enquote{[\ldots] allow the software
to be used for any purpose whatsoever with no obligation on the part of the
licensee to distribute the source code of derivative
works}\footcite[cf.][71]{Rosen2005a}. By this meaning, these clusters might be
referred as the \enquote{main categories} of (Open Source)
licenses\footcite[cf.][179]{Rosen2005a}. But one has to mind that they build an
antinomy inside of the set of Open Source Licenses\footnote{It is not suitable
to say, that \enquote{the Open Source License (OSL) is a reciprocal license} and
 \enquote{the Acadmic Free License (AFL) is the exact same license without the
 reciprocity provisions} (\cite[cf.][180]{Rosen2005a}): If the BSD license is an
 AFL and if an AFL can't be an OSL and if the OSI approves only OSLs, then the
 BSD license can't be an approved Open Source License. But it is
 (\cite[cf.][\nopage wp]{OSI2012b}).}.

Close to the clusters \emph{academic licenses} and \emph{reciprocal licenses} is
the grouping into \emph{permissive licenses}, \emph{weak copyleft licenses}, and
\emph{strong copyleft licenses}: Some authors name the set of \emph{academic
licenses} the \enquote{permissive licenses} and specify the \emph{reciprocal
licenses} as \enquote{restrictive licenses} because in this case - as
consequence of the embedded \enquote{copyleft} effect - the source code must be
published in case of modifications. And they additionally introduce the subset
of \enquote{strong restrictive licenses} which additionally require that an
(overarching) derivative work must be published under the same
license\footcite[cf.][57]{Buchtala2007a}. The next step is directly to talk
about Open Source Licenses without Copy lect, with strict Copy Left and those
with weak copy left.

On the base of these defintions we get the following licenses clusters:

But again, we have to state that this grouping does not allow to conclude to the
license fulfilling behavior: Even if both, the BSD license and the apache
license are permissive license, they can require differnt tasks for being
fulfilled. And indeed, they do so: The BSD license wants that the copyright note
to be published. But the apache license requires, that the conten of the notice
file must be shown to the user. These are similar tasks with similar purposes,
but finally they are different task.

And there is another difficulty with nearly all these labels of categories: they
are colored by the underling 'philosophical' positions: Permissive licenses are
permissive, because they allow companies to use the software with only some
minor requirements. On the other hand the restrictive licenses are restritive,
because they are limiting the action room of their users: they are not free to
use the programm without fulfilling more and harder restrictions.

But the intended meaning of the original author of the most restrictive license,
the GPL, is not to restrict the users, but to save the freedom in future. Zitat.




You may find taxonomies in your prefered magazins\footnote{see For example the
German Linux Magazine 04/05 2011
% TODO Linux Magazin 04/05:2011 wegen Taxonomie in bibtex aufnehmen und zitieren
} or in more or less specific legal literature\footnote{\ldots must be found
% TODO Taxonomien aus juristischer literature zitieren
}.

One of the most known license taxonomies is established by the grouping of the
'permissive' licenses, the 'weak copyleft licenses' and 'strong copyleft
licenses'\footnote{ \ldots belegen
% TODO permissive, weak & strong copyleft taxonomie belegen aus Buch
}:

% TODO Taxonomie permissive, weak, strong mit psztricks setzen

All these taxonomies are invented to simplify the talking about Open Source
licenses: One wants to talk about the groups instead of regarding each license.
And one wants to elaborate the internal structure of the amorph field of
licenses. Structuring by generalization is the first method of human beings to
adopt an area and to produce knowledge:

The main group is established by the 10 criteria of the Open Source Definition.
Each Open Source license must fit each of these 10 criteria for being an Open
Source license. These 10 criteria forms the external borders. So, for getting
internal groups of this cluster, one has to refer to other criteria. There exist
extrinsic criteria like 'being known' or 'being unknown' and intrinsic criteria
like 'being permissive', 'weak copylefted' or 'strong copyleft'.

The most known clustering 'permissive', 'weak copylefted' and 'strong
copylefted' refers to some consequences one has to respect for getting the right
to use the software. This is a problematic viewpoint. It seduces the users to
think that they have only to fulfill these conditions. But indeed, also for the
most permissive license one has to do specific things. So, with respect to
question what we have to get the right to use, to modify and/or to distribute
the software it is a bad solution to think in the categories of 'permissive',
'weak copylefted' and 'strong copylefted' Open Source licenses.

Nevertheless, the human beings needs structering elements for enabling
themselves to talk about an area. Hence, we should offer another possibility to
cluster the Open Source licenses:

We think, that in general, licenses have a common purpose: they should protect
someone or something against something\footnote{which lateron might be refined
by the type of methods they use}. This is based on the nature of the word
'protect' is a 3 valent verb: it links someone or something, who protects, to
someone or something, who is protected and both together to something against
the protector protects and against the otherone is protected. Licenses do so,
even Open Source Licenses: They can protect the user (receiver) of the software,
its' contributor resp. developer and/or distributor, and the software itself.
And they protect them against different threats. With respect to this viewpoint,
we can specify the Open Source licenses in a specific, purpose orientied way:

\begin{itemize}
  \item Firstly, the BSD Licenses protect the user against the loss of the right
  to use, to modify and/or to distribute the received copy of the source code or
  the binary - which directly depends on the Open Source Definition.
  Secondly they protect the contributor and/or distributor against warranty
  claims of the user, because they contain a 'No Warranty Clause'. Thirdly they
  protect distributed sources against a reclosing change of the
  license, because each modification and distribution must retain the existing
  copy right notes and the licensing remarks, so that distributing under another
  license is not allowed.
  
  But
  \item The MIT Licenses protect
\end{itemize}


All these specifications can also be covered by a table:

\begin{table}
\footnotesize
\caption{Open Source Licenses as Protectors}
\begin{center}

\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
  \multicolumn{2}{|c|}{\textit{Open}} &
  \multicolumn{12}{c|}{\textit{are protecting}}\\
\cline{3-14}
  \multicolumn{2}{|c|}{\textit{Source}} &
  \multicolumn{4}{c|}{ \textbf{Users}} &
  \multicolumn{3}{c|}{\textbf{Contributors}} &
  \multicolumn{5}{c|}{\textbf{Software}} \\
\cline{10-14}
  \multicolumn{2}{|c|}{\textit{Licenses}} &
  \multicolumn{4}{c|}{} &
  \multicolumn{3}{c|}{\tiny{(Distributors)}} &  
  not &
  \multicolumn{4}{c|}{distributed as} \\
\cline{3-9}\cline{11-14}
  \multicolumn{2}{|c|}{} &
  \multicolumn{4}{c|}{\scriptsize{\textit{who have already got}}} &
  \multicolumn{3}{c|}{\scriptsize{\textit{who spread Open}}} & 
  distri- &
  \multicolumn{2}{c|}{modified} &
  \multicolumn{2}{c|}{unmodified} \\
  \cline{11-14}
  \multicolumn{2}{|c|}{} &
  \multicolumn{4}{c|}{\scriptsize{\textit{sources or binaries}}} &
  \multicolumn{3}{c|}{\scriptsize{\textit{Source software}}} & 
  buted & 
 \footnotesize{sources} &
 \footnotesize{binaries} &
 \footnotesize{sources} &
 \footnotesize{binaries} \\
\cline{3-14}
  \multicolumn{2}{|c|}{} &
  \multicolumn{12}{c|}{\textit{against}}\\
\cline{3-14}
  \multicolumn{2}{|c|}{} &
  \multicolumn{3}{c|}{the loss of} & 
  \multirow{3}{*}{\rotatebox{270}{Patent Disputes}} &
  \multirow{3}{*}{\rotatebox{270}{Loss of Feedback}} & 
  \multirow{3}{*}{\rotatebox{270}{Warranty Claims}} & 
  \multirow{3}{*}{\rotatebox{270}{Patent Disputes}} & 
  \multicolumn{5}{c|}{}\\
% no seperator line 
  \multicolumn{2}{|c|}{} &
  \multicolumn{3}{c|}{the right to} &
  & & & &
  \multicolumn{5}{c|}{\footnotesize{Re-Closings of}}\\
\cline{3-5}
  \multicolumn{2}{|c|}{} & 
  \rotatebox{270}{use it} & 
  \rotatebox{270}{modify it} & 
  \rotatebox{270}{redistribute it} &
  &  &  &  &
  \multicolumn{5}{c|}{already Opened Software}\\
\hline
\hline
  APL & 2.0 & \checkmark  & \checkmark  & \checkmark & 
  - & - & - & - & - & - & - & - & - \\
\hline
  \multirow{2}{*}{BSD}\footnotemark & 3-Cl & \checkmark & \checkmark  & \checkmark  & 
    $\neg$ & $\neg$ & \checkmark & $\neg$  &
    $\neg$ & \checkmark  & $\neg$ & \checkmark & $\neg$ \\
\cline{2-14}
   & 2-Cl & \checkmark  & \checkmark  & \checkmark  & 
    $\neg$ & $\neg$ & \checkmark & $\neg$  &
    $\neg$ & \checkmark  & $\neg$ & \checkmark & $\neg$ \\
\hline
  MIT\footnotemark & 1.1 & \checkmark  & \checkmark  & \checkmark  &
  - & - & - & - & - & - & - & - & - \\
\hline
  MsPL & 1.1 & \checkmark  & \checkmark  & \checkmark  & 
  - & - & - & - & - & - & - & - & - \\
\hline
  PHP & 2.0 & \checkmark  & \checkmark  & \checkmark  &
  - & - & - & - & - & - & - & - & - \\
\hline
\hline
  EPL & 1.0 & \checkmark & \checkmark & \checkmark &
  - & - & - & - & - & - & - & - & - \\
\hline
  EUPL & 2.0 & \checkmark & \checkmark & \checkmark &
  - & - & - & - & - & - & - & - & - \\
\hline
  \multirow{2}{*}{LGPL} & 2.1 & \checkmark & \checkmark & \checkmark &
  - & - & - & - & - & - & - & - & - \\
\cline{2-14}
   & 3.0 & \checkmark & \checkmark & \checkmark &
   - & - & - & - & - & - & - & - & - \\
\hline
  \multirow{2}{*}{MPL} & 1.0 & \checkmark & \checkmark & \checkmark &
  - & - & - & - & - & - & - & - & - \\
\cline{2-14}
  & 2.0 & \checkmark & \checkmark & \checkmark &
  - & - & - & - & - & - & - & - & - \\
\hline
\hline
  \multirow{2}{*}{AGPL} & 2.1 & \checkmark & \checkmark & \checkmark &
   - & - & - & - & - & - & - & - & - \\
\cline{2-14}
   & 3.0 & \checkmark & \checkmark & \checkmark &
    - & - & - & - & - & - & - & - & - \\
\hline
  \multirow{2}{*}{GPL} & 2.1 & \checkmark & \checkmark & \checkmark &
   - & - & - & - & - & - & - & - & - \\
\cline{2-14}
  & 3.0 & \checkmark & \checkmark & \checkmark &
   - & - & - & - & - & - & - & - & - \\
\hline
\hline

\end{tabular}
\end{center}
\end{table}
\addtocounter{footnote}{-1}
\footnotetext{Berkeley Software Distribution [License]}
\stepcounter{footnote}
\footnotetext{Massuchat Institute of Technique [License]}

And the content of this classifying table can also be transfered into a mindmap:

\begin{tikzpicture}
\label{LICTAX}
\footnotesize

% (1.A) list of all licenses and their release numbers Level 5/6
\node[rectangle,draw,text width=1.4cm] (l0100) at (10,0.5)
{ \textit{BSD License} };
\node[text width=1.4cm] (l0101) at (12,0)
{ \scriptsize{3-Clauses} };
\node[text width=1.4cm] (l0102) at (12,1)
{ \scriptsize{2-Clauses} };
  
\node[rectangle,draw,text width=1.4cm] (l0200) at (11,2)
{ \textit{MIT License} }; 
\node[text width=0.4cm] (l0201) at (12.5,2) {\scriptsize{1.1}};
  
\node[rectangle,draw,text width=1.4cm] (l0300) at (12.5,3)
{ \textit{\textbf{AP}ache \textbf{L}icense}};
   \node[text width=0.4cm] (l0301) at (14,3) {\scriptsize{2.1}};

\node[rectangle,draw,text width=1.4cm] (l0400) at (13,4.5)
{ \textit{\textbf{M}icro\textbf{s}oft \textbf{P}ublic \textbf{L}icense} };
\node[text width=0.4cm] (l0401) at (14.5,4){\scriptsize{1.0}};
\node[text width=0.4cm,style=dotted] (l0402) at (14.5,5){\scriptsize{\textit{1.1}}};
  
\node[rectangle,draw,text width=1.4cm] (l0500) at (13,6)
{\textit{\textbf{P}ost\textbf{g}res \textbf{L}icense}};
\node[text width=0.4cm] (l0501) at (14.5,6){ \scriptsize{1.1}};
  
\node[rectangle,draw,text width=1.4cm] (l0600) at (13,7)
{\textit{PHP License}};
\node[text width=0.4cm] (l0601) at (14.5,7){\scriptsize{1.1}};
  
\node[rectangle,draw,text width=1.4cm] (l0700) at (13,8)
{ \textit{XXX License}};
\node[text width=0.4cm] (l0701) at (14.5,8){\scriptsize{1.1}};

\node[rectangle,draw,text width=1.4cm] (l0800) at (13,9.5)
{ \textit{\textbf{M}ozilla \textbf{P}ublic \textbf{L}icense}};
\node[text width=0.4cm] (l0801) at (14.5,9){\scriptsize{1.1}};
\node[text width=0.4cm] (l0802) at (14.5,10){\scriptsize{2.0}};

\node[rectangle,draw,text width=1.4cm] (l0900) at (13,11.5)
{\textit{\textbf{E}clipse \textbf{P}ublic \textbf{L}icense}};
\node[text width=0.4cm] (l0901) at (14.5,11) {\scriptsize{1.0}};
\node[text width=0.4cm,style=dotted] (l0902) at (14.5,12){\scriptsize{\textit{1.1}}};
 
\node[rectangle,draw,text width=1.5cm] (l1000) at (13,13.5)
{\textit{\textbf{E}uropean \textbf{P}ublic \textbf{L}icense}}; 
\node[text width=0.4cm] (l1001) at (14.5,13){\scriptsize{1.0}};
\node[text width=0.4cm,style=dotted] (l1002) at (14.5,14){\scriptsize{\textit{1.1}}};
  
\node[rectangle,draw,text width=1.4cm] (l1100) at (13,15.5)
{\textit{\textbf{L}esser \textbf{G}NU \textbf{P}ublic \textbf{L}icense}};

\node[text width=0.4cm] (l1101) at (14.5,15){\scriptsize{2.1}};
\node[text width=0.4cm] (l1102) at (14.5,16){\scriptsize{3.0} };

\node[rectangle,draw,text width=1.4cm] (l1200) at (13,17.5)
{\textit{\textbf{G}NU \textbf{P}ublic \textbf{L}icense}};

\node[text width=0.4cm] (l1201) at (14.5,17){\scriptsize{2.1}};
\node[text width=0.4cm] (l1202) at (14.5,18){\scriptsize{3.0} };

\node[rectangle,draw,text width=1.4cm] (l1300) at (13,19.5)
{ \textit{\textbf{A}ffero \textbf{G}NU \textbf{P}ublic \textbf{L}icense}};
\node[text width=0.4cm, style=dotted] (l1301) at (14.5,19){\scriptsize{2.1}};
\node[text width=0.4cm] (l1302) at (14.5,20){\scriptsize{3.0}};

% 2. the clustering concepts of licenses (level 4)
\node[rectangle,draw,text width=2.3cm] (n0100) at (10,8)
 { \textit{protecting the user, the con\-tri\-butor \& the initial code}\\
   \tiny{Permissive Licenses}      
 };

\node[rectangle,draw,text width=2.3cm] (n0200) at (10,11.5)
{ \textit{protecting the user, the con\-tri\-butor, the
  initial code, \& all di\-rect de\-ri\-va\-tions}\\
  \tiny{Weak Copyleft}        
};

\node[rectangle,draw,text width=2.3cm] (n0300) at (10,16.5)
{ \textit{protecting the user, the con\-tri\-bu\-tor, the 
  initial code, all di\-rect de\-ri\-va\-tions \& the 
  (in\-di\-rect\-ly de\-ri\-ved) on-top-deve\-lop\-ments}\\ 
  \tiny{Strong Copyleft}    
 };

% 3. the threats (level 3)
\node[ellipse,draw,text width=1.6cm] (c110000) at (4.5,0)
{ \textbf{\textit{Patent Disputes}}};

\node[ellipse,draw,text width=1.6cm] (c120000) at (4.5,2)
{ \textbf{\textit{Loss of Rights}} };

\node[ellipse,draw,text width=1.6cm] (c210000) at (4.5,4)
{ \textbf{\textit{Warranty Claims}} };
 
\node[ellipse,draw,text width=1.6cm] (c220000) at (4.5,6)
{ \textbf{\textit{Loss of Feeback}}};

\node[ellipse,draw,text width=0.4cm] (c311000) at (6.2,8)
{ \tiny{\textit{\textbf{clos\-ings}}}};

\node[ellipse,,draw,text width=0.4cm] (c321000) at (6.2,10)
{ \tiny{\textit{\textbf{clos\-ings}}} };

\node[ellipse,,draw,text width=0.4cm] (c331000) at (6.2,12)
{ \tiny{\textit{\textbf{clos\-ings}}} };

\node[ellipse,,draw,text width=0.4cm] (c341000) at (6.2,14)
{ \tiny{\textit{\textbf{clos\-ings}}} };

\node[ellipse,,draw,text width=0.4cm] (c351000) at (6.2,16)
{ \tiny{\textit{\textbf{clos\-ings}}} };

\node[ellipse,,draw,text width=1.6cm] (c411000) at (6.2,19)
{ \textit{\textbf{clos\-ings}} };


% 4. the subtypes of protected entities (level 2)
\node[ellipse,draw,text width=1.5cm] (c310000) at (3,8)
 { \scriptsize{un\-modified} \textbf{Sources}};

\node[ellipse,draw,text width=1.5cm] (c320000) at (3.25,10)
 { \scriptsize{un\-modified} \textbf{Binaries}};

\node[ellipse,draw,text width=1.2cm] (c330000) at (3.5,12)
 { \scriptsize{modified} \textbf{Sources}};

\node[ellipse,draw,text width=1.4cm] (c340000) at (3.25,14)
 { \scriptsize{modified} \textbf{Binaries}};

\node[ellipse,draw,text width=1.4cm] (c350000) at (3,16)
 { \scriptsize{part of \textbf{On-Top-Develop\-ments}}};


% 5. the protected entities (level 1)
\node[ellipse,draw,text width=1cm] (c100000) at (1,1)
 { \textbf{Users} };

\node[ellipse,draw,text width=0.8cm] (c200000) at (1,5)
 { \textbf{Con\-tribu\-tors}};

\node[ellipse,draw,text width=0.8cm] (c300000) at (1,12)
 { distri\-buted \textbf{Soft\-ware}};
 
\node[ellipse,draw,text width=2.2cm] (c400000) at (1,19)
 { un\-distri\-buted \textbf{Soft\-ware}}; 

% 6. main node (leve 0)
\node[ellipse,draw,text width=1.3cm] (c000000) at (0,8)
{ \textbf{Open Source License}};

% a linking Licenses to their release numbers (Linking level 5 to 6)
\foreach \father/\daughter in {
  l0100/l0101/,
  l0100/l0102/,
  l0200/l0201/,   
  l0300/l0301/,
  l0400/l0401/,
  l0400/l0402/,
  l0500/l0501/,
  l0600/l0601/,
  l0700/l0701/,
  l0800/l0801/,
  l0800/l0802/,
  l0900/l0901/,
  l0900/l0902/,
  l1000/l1001/,
  l1000/l1002/,
  l1100/l1101/,
  l1100/l1102/,
  l1200/l1201/,
  l1200/l1202/,
  l1300/l1301/,
  l1300/l1302/
  }
  \draw[dashed] (\father) to  (\daughter) ;

% b) linking Licenses to license concepts (Linking level 5 to 4)
\foreach \father/\daughter/\outangle/\inangle in {
  n0100/l0100/270/150,       
  n0100/l0200/280/155,
  n0100/l0300/290/160,
  n0100/l0400/300/165,
  n0100/l0500/310/150,
  n0100/l0600/340/160,
  n0100/l0700/360/180,
  n0200/l0800/300/160,
  n0200/l0900/340/170,
  n0200/l1000/20/190,
  n0200/l1100/60/200,
  n0300/l1200/40/180,
  n0300/l1300/80/180 
  }
  %\draw[dashed] (\father) to [out=\outangle,in=\inangle] (\daughter) ;
  \draw[dashed] (\father) to  (\daughter) ;

% c) linking license concepts to the threats against they protect
% c.1) strong copyleft licenses
\foreach \father/\daughter/\outangle/\inangle in {
  c351000/n0300/0/180,
  c341000/n0300/45/190,
  c331000/n0300/50/200,
  c321000/n0300/55/210,
  c311000/n0300/60/220,
  c220000/n0300/25/225,
  c210000/n0300/25/230,
  c120000/n0300/25/235
  }
  \draw[<-,color=blue] (\father) to [out=\outangle,in=\inangle] (\daughter) ;
% c.2) weak copyleft licenses
\foreach \father/\daughter/\outangle/\inangle in {
  c341000/n0200/330/170,
  c331000/n0200/0/180,
  c321000/n0200/0/180,
  c311000/n0200/20/190,
  c220000/n0200/15/220,
  c210000/n0200/15/230,
  c120000/n0200/15/235
  }
  \draw[<-,color=cyan] (\father) to [out=\outangle,in=\inangle] (\daughter) ;
% c.3) permissive licenses
\foreach \father/\daughter/\outangle/\inangle in {
  c331000/n0100/355/150,
  c311000/n0100/0/180,
  c210000/n0100/5/210,
  c120000/n0100/10/230
  }
  \draw[<-,color=red] (\father) to [out=\outangle,in=\inangle] (\daughter) ;
%c.4 agpl license
\foreach \father/\daughter/\outangle/\inangle in {
  c411000/l1300/0/180    
}
  \draw[<-,color=green] (\father) to [out=\outangle,in=\inangle] (\daughter) ;


%d linking protected entities, their subtypes and the the relations
\foreach \father/\daughter/\edgetext/\outangle/\inangle in {
  c000000/c100000/protecting/260/120,
  c100000/c110000/against/360/180,
  c100000/c120000/against/360/180,
  c000000/c200000/protecting/270/180,
  c200000/c210000/against/0/180,
  c200000/c220000/against/0/180,
  c000000/c300000/protecting/90/230,
  c300000/c310000/as/300/180,
  c300000/c320000/as/330/180,
  c300000/c330000/as/0/180,
  c300000/c340000/as/30/180,
  c300000/c350000/as/60/180,
  c000000/c400000/protecting/100/240,
  c400000/c411000/against/0/180        
}
  \draw[->,dotted,
    decoration={text along path,
              text align={center},
              text={|\itshape|\edgetext}},
              postaction={decorate},] (\father) to [out=\outangle,in=\inangle] (\daughter) ;

\foreach \father/\daughter/\edgetext/\outangle/\inangle in {
  c310000/c311000/against/0/180,
  c320000/c321000/against/0/180,
  c330000/c331000/against/0/180,
  c340000/c341000/against/00/180,
  c350000/c351000/against/0/180        
}
  \draw[->,dotted,
    decoration={text along path,
              text align={center},
              text={|\itshape \tiny|\edgetext}},
              postaction={decorate},] (\father) to [out=\outangle,in=\inangle] (\daughter) ;

%f linking the patent clauses
\foreach \father/\daughter/\outangle/\inangle in {
  c110000/l1302/0/295,
  c110000/l0401/0/360,
  c110000/l0301/0/360   
}
  \draw[<-,color=gray] (\father) to [out=\outangle,in=\inangle] (\daughter) ;

\end{tikzpicture}


Finally, one could generate new groups of Open Source license, new classes, like
'user protecting licenses'\footnote{all of them because all of them have to
fulfill the OSD}, 'patent disputes abwehrende licenses', 'modified \ldots'.

But one has to know: all of these grouping viewpoints do not allow to conclude,
that all members of a group can be respected by fulfilling the same
requirements. This would only be possible, if the grouping criteria would
directly refer to the fulfilling tasks. And indeed, nearly all Open Source
licenses do differ with respect to these criteria, even if the differences are
very small, they can't be neglected\footnote{Pars pro toto: Both, the BSD
license and the Apache license require, that you give hint to the developers of
the application. But in case of the BSD license you xýou have to \ldots. In case
of the Apache license you have exactly to present the content of the notice file
distributed together with the application.}. So: reflecting on possible classes
of Open Source licenses is a got method to become familiar with the area of Open
Source licenses. But it is not a method to determine, what one has to do for
getting the right to use the software. For getting these information, one has to
consider each single license.


%\bibliography{../../../bibfiles/oscResourcesEn}
