% Telekom osCompendium 'for being included' snippet template
%
% (c) Karsten Reincke, Deutsche Telekom AG, Darmstadt 2011
%
% This LaTeX-File is licensed under the Creative Commons Attribution-ShareAlike
% 3.0 Germany License (http://creativecommons.org/licenses/by-sa/3.0/de/): Feel
% free 'to share (to copy, distribute and transmit)' or 'to remix (to adapt)'
% it, if you '... distribute the resulting work under the same or similar
% license to this one' and if you respect how 'you must attribute the work in
% the manner specified by the author ...':
%
% In an internet based reuse please link the reused parts to www.telekom.com and
% mention the original authors and Deutsche Telekom AG in a suitable manner. In
% a paper-like reuse please insert a short hint to www.telekom.com and to the
% original authors and Deutsche Telekom AG into your preface. For normal
% quotations please use the scientific standard to cite.
%
% [ Framework derived from 'mind your Scholar Research Framework' 
%   mycsrf (c) K. Reincke 2012 CC BY 3.0  http://mycsrf.fodina.de/ ]
%


%% use all entries of the bibliography
%\nocite{*}


\chapter{Introduction}

% Abstract
\footnotesize \begin{quote}\itshape This chapter shortly describes the idea of
the OSLiC, the way it should be used, and the way it can be read - what indeed
is not completely the same.
\end{quote}
\normalsize{}

% Content
This book focuses on only one issue: \emph{What do we have to do for acting
according to the licenses of those \emph{Open Source Software} we use?} The
\emph{Open Source License Compendium} wants to answer this question reliably -
in a simply to use and easily to understand manner. Thus, it is not another book
on \emph{Open Source} in ge\-ne\-ral\footnote{Meanwhile, there are tons of
literature dealing with Open Source. By improving your knowledge on the base of
such books and articles you might get lost in literature: our list of secondary
literature may adumbrate this 'danger of being overwhelmed'. But nevertheless,
our bibliography at the end of the OSLiC is not complete. Moreover, it's not
intended to be complete. It's only an extract which represents the background
knowledge we did not directly quoted in the OSLiC. If we were pressured to
indicate two books for getting a good survey on the topic \emph{Open Source
(Licenses)} we would name (a) the 'Rebel Code' (\cite[for a German version
cf.][\nopage passim]{Moody2001a} - \cite[for an English version
cf.][passim]{Moody2002a}) and (b) the 'legal basic conditions'
(\cite[cf.][\nopage passim]{JaeMet2011a}). But fortunately, we are not pressured
to do so.}. It shall be no more than a reliable tool to simplify the license
compliant behavior.

This compendium was evoked by a challenge of \emph{Deutsche Telekom AG} and some
of its software developers and project managers: Naturally, they want to behave
license compliantly. But they could not find a reference text which simply lists
what they concretely had to do to fulfill the licenses of that Open Source, they
currently used.

As some of these co-workers in Telekom projects, even we - the initial authors
of the OSLiC - did not want to become Open Source license experts only for being
able to use Open Source Software in a regular manner. We did not want to become
lawyers. We simply wanted to do in a simplier way, what in those days claimed
much time and many resources. We were searching for a clear guidance instead of
having to determine a correct way through the djungel of Open Source Licenses -
over and over again, project for project. We loved to use the high-quality Open
Source Software to improve our performance. We liked to use it legally. But we
did not like to laboriously discuss the juridical constraints of the many and
different Open Source Licenses.

What we needed, was a simply to use handout which would lead us without any
detours to executable lists of working items. We wished to get To-Do-Lists,
dedicated to our usecases and our licenses. We needed reliable lists of tasks we
only had to execute for being sure that we were acting according to the Open
Source License. When we started, such a compendium did not exist.

For solving this problem our company took three decisions:

The first decision our company came to, was to support a small group of
employees to act as \emph{a board of Open Source License experts}: They should
offer a service for the whole company. Projects, managers, and developers should
be enabled to ask this board what they have to do for fulfilling a specific Open
Source License under specific circumstances. And this board should answer with
reliable to-do lists, whose executions would assure that the requestors are
acting according to the corresponding Open Source Licenses. The idea behind this
decision was simple. It would save costs and quality if one had a central group
of experts instead of being obliged to select (and to train) developers - over
and over again and again, for every project new. So, the \emph{OSRB} - the
\emph{Telekom Open Source Review Board} - was founded as an internal expert
group - as a self-organizing, bottom up driven community.

The second decision our company took, was to allow this \emph{Telekom OSRB} to
collect their results systematically . The idea behind this decision was also
simple: The more the internal service would become known, the more the workload
would increase: the more work, the more recources, the more costs. So, it was a
cost saving idea, to enable the requestors to find their answer by themselves -
but simply without becoming licenses experts: In the default cases, they should
find their answers in a compendium instead of making it necessary, to let their
work being analyzed by the OSRB. The planned \emph{Telekom Open Source License
Compendium} should preserve the Telekom to increase the number of OSRB members in
the future.

The third decision our company reached, was to allow the \emph{Telekom OSRB} to
elaborate the compendium in that mode of cooperation, Open Source projects used
to do. Again, a simple reason evoked this ruling: If in the future - as a rule -
not the reviewing OSRB, but a only manual should assure the Open Source License
compliant behavior of projects, programmers and managers, this book had of
course to be particularily reliable. There is a known feature of the Open Source
working model: the ongoing review by the cooperating community increases the
quality. Therefore, the decision, not only to write an internal 'Telekom
handout', but to enable the whole community to use, to modify and to
redistribute a broader \emph{Open Source License Compendium}, was a decision for
improving the quality. Thus, the \emph{OSRB} published the \emph{OSLiC} as a set
von LaTex Sources. It decided to make them accessible via the open repository
github\footnote{Get the code by using the link
\texttt{https://github.com/dtag-dbu/oslic}; get project information by
\texttt{http://dtag-dbu.github.com/oslic/} or by
\texttt{http://www.oslic.org/}.}. And it licensed the OSLiC under Creative
Commons Attribution-ShareAlike 3.0 Germany License\footnote{ This text is
licensed under the Creative Commons Attribution-ShareAlike 3.0 Germany License
(\texttt{http://creativecommons.org/licenses/by-sa/3.0/de/}): Feel free
\enquote{to share (to copy, distribute and transmit)} or \enquote{to remix (to
adapt)} it, if you \enquote{[\ldots] distribute the resulting work under the
same or similar license to this one} and if you respect how \enquote{you must
attribute the work in the manner specified by the author(s) [\ldots]}):
In an internet based reuse please mention the initial authors in a suitable
manner, name their sponsor \textit{Deutsche Telekom AG} and link it to
\texttt{http://www.telekom.com}. In a paper-like reuse please insert a short
hint to \texttt{http://www.telekom.com}, to the initial authors, and to their
sponsor \textit{Deutsche Telekom AG} into your preface. For normal quotations
please use the scientific standard to cite.}.

But to publish the \emph{OSLiC} as a free book has another important meaning -
at least for the \emph{Telekom OSRB}: It is also intended to be a thankful
\emph{Giving Back} to the \emph{Open Source Community} which has enriched and
simplified the life of so many employees and companies over so many years.

Howsoever, overall, the OSLiC follows five principles:

\begin{description}
  \item[To-do lists as the core, discussions around them]: Based on simply to
  gather information concerning the concrete use of a piece of Open Source
  Software and its license, the OSLiC shall offer a simply processable finder
  which leads the requestor to the relevant, license compliance assuring to-do
  list. Additionally, all these elements of the OSLiC should comprehensibly
  be introduced and discussed without disturbing the usage itself.

  \item[Quotations with thoroughly specified sources]\label{QuotationPrinciple}:
  The OSLiC shall be revisable and reliable. It shall comprehensibly argue and
  explictly specify why it overtakes which information from whom in which
  version and why\footnote{For that purpose, we are using an 'old-fashioned'
  bibliographic style presented footnotes, instead of endnotes or inline-hints.
  We want to enable the users to review or to ignore our comments and hints just
  as they prefer to do - but on all accounts without being disturbed by large
  inline comments or frequent page turnings. We know that modern writer guides
  prefer less 'noisy' styles (\cite[pars pro toto cf.][\nopage
  passim]{Mla2009a}). But for a reliable usage - challenged by the often
  modified internet sources - these methods are still a little imprecize (for
  details $\rightarrow$ \enquote{sec:QuotationAppendix}, pp.
  \pageref{sec:QuotationAppendix} . For a short motivation of the style used in
  the OSLiC \cite[cf.][\nopage passim]{Reincke2012a}. For a more elaborated
  legitimizing version \cite[cf.][\nopage passim]{Reincke2012b}) }.

 \item[Not clearing out the forest land, but cutting out a swathe]: The OSLiC
  has to deal with licenses and their legal aspects, no doubt. But it shall not
  discuss all details of all aspects. It shall focus on one possible way to act
  according a license in a specific usecase - even it is known, that there might
  be alternatives\footnote{The OSLiC shall not counsel projects with respect to
  their specific needs. This must remain the tasks lawyers and legal experts.
  They can answer the question, whether a project under its' specfic conditions
  could also / better use another way to fulfill the Open Source license.}.
  
  \item[Take the license text seriously]: The OSLiC shall not give general
  lectures on legal discussions. Much less, it shall participate in them. It
  shall only find one reliable way for each license and each usecase to fulfill
  the license. The main source for this analyze shall be the exact reading of
  the Open Source Licenses themselves - based and supported by the
  interpretation of benevolent lawyers and rational argueing software
  developers. The OSLiC shall respect, that Open Source Licenses are written for
  software developers (and sometimes by developers).
  
  \item[Trust the swarm]: The OSLiC shall be open for improvements and
  adjustments encouraged an stimulated also by other people than employees of
  \emph{Deutsche Telekom AG}.
\end{description}

And based on these principles the OSLiC offers two modes to be used:

Firstly and mostly the readers wish to find those to-do list simply and quickly
which fit their needs. Here is the corresponding process\footnote{For the well
known 'quick and dirty hackers' - as we tend to be, too - we have integrated a
shortcut: If you are already knowing the license of that Open Source package you
want to use and if you are very familiar with the meaning of the Open Source Use
Cases we have defined, then you might directly jump to the corresponding license
specific chapter, without 'struggling' with \textbf{OSLiC 5 query form}
($\rightarrow$ p. \pageref{OSLiCStandardFormForGatheringInformation}), the
taxonomic \textbf{Open Source Use Case Finder} ($\rightarrow$
\pageref{OSLiCUseCaseFinder}) or the \textbf{O}pen \textbf{S}ource \textbf{U}se
\textbf{C}ase page ($\rightarrow$ \pageref{OSUCList}ff.): Each of the Open
Source License specficic chapters starts with a license specific finder offering
a set of license specific use cases - which according to the complexity of the
license - in some cases could be stripped down. But the disdadvantage of this
method is that you have to apply your knowledge about the use cases and their
side effects by your own, without the systematic control of the full OSLiC
process as it is presented here.
}:

\tikzstyle{decision} = [diamond, draw, fill=gray!20, 
    text width=4.5em, text badly centered, node distance=4cm, inner sep=0pt]

\tikzstyle{preparation} = [rectangle, draw, fill=gray!30, 
    text width=10em, text centered, rounded corners, minimum height=4em]
 
\tikzstyle{lprocs} = [rectangle, draw, fill=gray!40, 
    text width=10em, text centered, rounded corners, minimum height=4em]
    
\tikzstyle{processing} = [rectangle, draw, fill=gray!40, node distance=2.4cm,
    text width=15em, text centered, rounded corners, minimum height=4em]
    
\tikzstyle{line} = [draw, -latex']

\tikzstyle{cloud} = [draw, ellipse, text width=6em, text centered, fill=gray!10]
 
    
\begin{tikzpicture}[node distance =1.9cm, auto]
\footnotesize
    % Place nodes
    
  \node [cloud] (start) at (1,10) 
    {$\forall$ your \\ Open Source \\ components};
  \node [preparation] (select) at (5,10) 
    {select your next Open Source component};     
  \node [preparation,  below of=select] (analyze) 
    {analyze its' role in the software architecture and 
    determine the use of the app as whole};  
  \node [preparation,  below of=analyze] (determine) 
    {determine its Open Source License};
  \node [lprocs,  below of=determine] (fillin)
    {\textbf{fill in the 5 query form} ($\rightarrow$ p.
    \pageref{OSLiCStandardFormForGatheringInformation})};
    
  \node [decision, right of=fillin] (success) {success?};
  
  \node [processing,  below of=success] (traverse)
    {\textbf{traverse the} taxonomic \textbf{Open Source Use Case Finder}
    ($\rightarrow$ \pageref{OSLiCUseCaseFinder}) and jump to the indicated
    \textbf{O}pen \textbf{S}ource \textbf{U}se \textbf{C}ase page ($\rightarrow$
    \pageref{OSUCList}ff.)};
    
  \node [processing,  below of=traverse] (find)
    {\textbf{Determine} the page of \textbf{the license and use case specific to-do list}
    being presenetd in the license specific chapter};
 
  \node [processing,  below of=find] (process)
    {Jump to the indicated page and \textbf{process the license and use case specific
    to-do list} ($\rightarrow$ \pageref{OSUCToDoLists}ff.)};
    
  \node [decision, right of=process] (other) {more?};
  \node [cloud, below of=other] (stop) {stop};

  \path [line] (start) -- (select);  
     
  \path [line] (select) -- (analyze);      
  \path [line] (analyze) -- (determine);         
  \path [line] (determine) -- (fillin);
  \path [line] (fillin) -- (success);
  
  \path [line] (success) |- node [near start] {no} (analyze);
  \path [line] (success) -- node [near start] {yes} (traverse);             
  
  \path [line] (traverse) -- (find);              
  \path [line] (find) -- (process);
  \path [line] (process) -- (other);

  \path [line] (other) |- node [near start] {yes} (select);
  \path [line] (other) -- node [near start] {no} (stop);                      

\end{tikzpicture}

Secondly, the readers might wish to comprehend the whole analysis. So, we
shortly discuss Open Source Licenses taxonomies as base of license compliant
behavior\footnote{$\rightarrow$ \enquote{\nameref{sec:LicenseTaxonomies}}, pp.
\pageref{sec:LicenseTaxonomies}}. We consider some side effects with
relation to act according to the Open Source Licenses\footnote{$\rightarrow$
\enquote{\nameref{sec:SideEffects}}, pp. \pageref{sec:SideEffects}}. And we
study the structure of Open Source Use Cases\footnote{$\rightarrow$
\enquote{\nameref{sec:OSUCdeduction}}, pp. \pageref{sec:OSUCdeduction}}.

So, let's close our introduction by using, modifying, and (re)distributing a well
known wish of a well known man: Happy (Legally) Hacking.

%\bibliography{../../../bibfiles/oscResourcesEn}
