% Telekom osCompendium 'for being included' snippet template
%
% (c) Karsten Reincke, Deutsche Telekom AG, Darmstadt 2011
%
% This LaTeX-File is licensed under the Creative Commons Attribution-ShareAlike
% 3.0 Germany License (http://creativecommons.org/licenses/by-sa/3.0/de/): Feel
% free 'to share (to copy, distribute and transmit)' or 'to remix (to adapt)'
% it, if you '... distribute the resulting work under the same or similar
% license to this one' and if you respect how 'you must attribute the work in
% the manner specified by the author ...':
%
% In an internet based reuse please link the reused parts to www.telekom.com and
% mention the original authors and Deutsche Telekom AG in a suitable manner. In
% a paper-like reuse please insert a short hint to www.telekom.com and to the
% original authors and Deutsche Telekom AG into your preface. For normal
% quotations please use the scientific standard to cite.
%
% [ Framework derived from 'mind your Scholar Research Framework' 
%   mycsrf (c) K. Reincke 2012 CC BY 3.0  http://mycsrf.fodina.de/ ]
%


%% use all entries of the bibliography
%\nocite{*}

%TODO MM1 Ich würde davon absehen Open Source mit Großbuchstaben zu schreiben. Es ist zwar ein
%TODO MM1 stehender Begriff, aber kein Eigenname, außer als Teil eines Titels wie OSLiC o.ä.
%TODO MM1 Das gilt dann auch für alle erweiterten Begriffe wie Open Source Software oder
%TODO MM1 Open Source License etc.

\chapter{Introduction}

% Abstract
\footnotesize \begin{quote}\itshape
This chapter briefly describes the idea behind the OSLiC, the way it should be
used and the way it can be read - which is indeed not quite the same.
\end{quote}
\normalsize{}

% Content
This book focuses on just one issue: \emph{What needs to be done in order to
comply with the licenses of the \emph{Open Source Software} we are using?} The
\emph{Open Source License Compendium} aims at reliably answering this question -
in a simple and easy to understand manner. However, it is not just another book
on \emph{Open Source} in ge\-ne\-ral\footnote{Meanwhile, there are tons of
literature dealing with Open Source. By expanding your knowledge by means of
books and articles you might get lost in literature: our list of secondary
literature may adumbrate this 'danger of being overwhelmed'. But nevertheless,
our bibliography at the end of the OSLiC is not complete. Moreover, it is not
intended to be complete. It is only an extract representing the background
information we did not directly cite in the OSLiC. If we were forced to indicate
two books for attaining a good overview on the topic of \emph{Open Source
(Licenses)} we would name (a) the 'Rebel Code' (\cite[for a German version
cf.][\nopage passim]{Moody2001a} - \cite[for an English version
cf.][passim]{Moody2002a}) and (b) the 'legal basic conditions'
(\cite[cf.][\nopage passim]{JaeMet2011a}). But fortunately, we are not forced to
do so.}, the intention is, rather, for it to be a tool for achieving license
conformity.

This compendium was created out of the necessity at \emph{Deutsche Telekom AG}
and in some of the software projects: Of course developers and project managers
want to observe each and every license obligation. Unfortunately, there is no
reference text which simply lists what precisely must be done in order to comply
with the license of that piece of Open Source being used.

As some of these co-workers in Telekom projects, even we - the initial authors
of the OSLiC - did not want to become Open Source License experts only for being
able to use Open Source Software in a normal way. We did not want to become
lawyers. We just wanted simplify what used to be time consuming and require a
lot of resources. We were searching for clear guidance instead of having to
determine a correct way through the jungle of Open Source Licenses - over and
over again, project for project. We loved using the high-quality Open Source
Software to improve our performance. We liked using it properly. But we did not
like to laboriously discuss the legal constraints of the many and different Open
Source Licenses.

What we needed, was an easy-to-use handout which would directly provide us with
executable lists of work items. We wanted To-Do-Lists tailored to our use cases
and our licenses. We needed reliable lists of tasks we only had to execute for
being sure that we were in accordance with the open Source License. When we
started out, such a compendium did not exist.

For solving this problem our company took three decisions:

The first decision our company arrived at was to support a small group of
employees to act as \emph{a board of Open Source License experts}: They should
offer a service to the whole company. Projects, managers, and developers should
be able to ask this board what they have to do for complying with a specific
open Source License under specific circumstances. And this board should return
authoritative to-do lists, the execution of which would assure that the
requestors are acting according to the corresponding Open Source License. The
idea behind this decision was simple. It would save cost and increase quality if
one had one central group of experts instead of being obliged to select (and to
train) developers - over and over again, for every new project. So, the
\emph{OSRB} - the \emph{Telekom Open Source Review Board} - was founded as an
internal expert group - as a self-organizing, bottom-up driven community.

The second decision our company took, was to allow this \emph{Telekom OSRB} to
%TODO MM1 Die Aussage des ersten Satzes ist mir nicht klar.
collect their results systematically. The idea behind this decision was also
simple: The more the internal service becomes known, the more the workload will
increase: the more work, the more recources, the more costs. So, the idea was to
save costs and enable the requestors to find answers by themselves without
becoming license experts: For all default cases, they should find an answer in
the compendium instead of having to request that their work be analyzed by the
OSRB. Thus, the planned \emph{Telekom Open Source License Compendium} prevents
Telekom from having to increase the number of OSRB members in the future.

The third decision our company reached, was to allow the \emph{Telekom OSRB} to
create the compendium in the same mode of cooperation used in Open Source
projects. Again, a simple reason evoked this ruling: If in the future - as a
rule - not a reviewing OSRB, but a simple manual should assure the Open Source
License conformity for projects, programmers and managers, this book had of
course to be particularily authoritative. There is a known feature of the Open
Source working model: the ongoing review by the cooperating community increases
the quality. Therefore, the decision not only to write an internal 'Telekom
handout', but to enable the whole community to use, modify and redistribute a
broader \emph{Open Source License Compendium}, was a decision for improving
quality. Consequently, the \emph{OSRB} decided to publish the \emph{OSLiC} as a
set of LaTex sources, publicly available via the open repository
github\footnote{Get the code by using the link
\texttt{https://github.com/dtag-dbu/oslic}; get project information by
\texttt{http://dtag-dbu.github.com/oslic/} or by
\texttt{http://www.oslic.org/}.}. And it licensed the OSLiC under Creative
Commons Attribution-ShareAlike 3.0 Germany License\footnote{ This text is
licensed under the Creative Commons Attribution-ShareAlike 3.0 Germany License
(\texttt{http://creativecommons.org/licenses/by-sa/3.0/de/}): Feel free
\enquote{to share (to copy, distribute and transmit)} or \enquote{to remix (to
adapt)} it, if you \enquote{[\ldots] distribute the resulting work under the
same or similar license to this one} and if you respect how \enquote{you must
attribute the work in the manner specified by the author(s) [\ldots]}):
In an internet based reuse please mention the initial authors in a suitable
manner, name their sponsor \textit{Deutsche Telekom AG} and link it to
\texttt{http://www.telekom.com}. In a paper-like reuse please insert a short
hint to \texttt{http://www.telekom.com}, to the initial authors, and to their
sponsor \textit{Deutsche Telekom AG} into your preface. For normal citations
please use the scientific standard.}.

But to publish the \emph{OSLiC} as a free book has another important connotation -
at least for the \emph{Telekom OSRB}: It is also intended to be an appreciative
\emph{giving back} to the \emph{Open Source community} which has enriched and
simplified the life of so many employees and companies over so many years.

Altogether, the OSLiC follows five principles:

\begin{description}
  \item[To-do lists as the core, discussions around them]: Based on simple
  gathering of information concerning the concrete use of a piece of Open Source
  software and its license, the OSLiC shall offer an easy-to-use finder taking
  the requestor to the respecvtive to-do list for ensuring license conformity.
  In addition, all these elements of the OSLiC should comprehensibly be
  introduced and discussed without disturbing the usage itself.

  \item[Quotations with thoroughly specified sources]\label{QuotationPrinciple}:
  The OSLiC shall be revisable and authoritative. It shall comprehensibly argue
  and explictly specify why it adopts which information from whom in which
  version and why\footnote{For that purpose, we are using 'old-fashioned'
  bibliographic style footnotes, instead of endnotes or inline-hints.
  We want to enable the users to review or to ignore our comments and hints just
  as they prefer - but on all accounts without being disturbed by large inline
  comments or frequent page turnings. We know that modern writer guides prefer
  less 'noisy' styles (\cite[pars pro toto cf.][\nopage passim]{Mla2009a}). But
  for a reliable usage - challenged by the often modified internet sources -
  these methods are still a little imprecise (for details $\rightarrow$
  \enquote{sec:QuotationAppendix}, pp. \pageref{sec:QuotationAppendix} . For a
  short motivation of the style used in the OSLiC \cite[cf.][\nopage
  passim]{Reincke2012a}. For a more elaborated legitimizing version
  \cite[cf.][\nopage passim]{Reincke2012b}) }.

 \item[No clearing the forest, but cutting a swath]: The OSLiC
  has to deal with licenses and their legal aspects, no doubt. But it shall not
  discuss all details of every aspect. It shall focus on one possible way to
  comply with a license in a specific usecase - even it is known that there
  might be alternatives\footnote{The OSLiC shall not counsel projects with
  respect to their specific needs. This must remain the task for lawyers and
  legal experts. They can assess whether a project with its specfic conditions
  could also / better use another way of conforming to the Open Source
  license.}.
  
  \item[Take the license text seriously]: The OSLiC shall not give general
  lectures on legal discussions, much less will it participate in them. It shall
  only find one dependable way for each license and each use case to comply with
  the license. The main source for this analysis shall be careful observation of
  the Open Source Licenses themselves - based on and supported by the
  interpretation of benevolent lawyers and rational argueing software
  developers. The OSLiC shall respect that Open Source Licenses are written for
  software developers (and sometimes by developers).
  
  \item[Trust the swarm]: The OSLiC shall be open for improvements and
  adjustments encouraged an stimulated also by other people than employees of
  \emph{Deutsche Telekom AG}.
\end{description}

Based on these principles the OSLiC offers two modes for being used:

First and foremost the readers expect to simply and quickly find those to-do
lists fitting their needs. Here is the respective process\footnote{For the well
known 'quick and dirty hackers' - as we tend to be, too - we have integrated a
shortcut: If you already know the license of the Open Source package you want to
use and if you are very familiar with the meaning of the Open Source use cases
we defined, then you might directly jump to the corresponding license specific
chapter, without 'struggling' with \textbf{OSLiC 5 query form} ($\rightarrow$ p.
\pageref{OSLiCStandardFormForGatheringInformation}), the taxonomic \textbf{Open
Source Use Case Finder} ($\rightarrow$ \pageref{OSLiCUseCaseFinder}) or the
\textbf{O}pen \textbf{S}ource \textbf{U}se \textbf{C}ase page ($\rightarrow$
\pageref{OSUCList}ff.): Each of the Open Source License specficic chapters
starts with a license specific finder offering a set of license specific use
cases - which according to the complexity of the license - in some cases could
be stripped down. But the disdadvantage of this method is that you have to apply
your knowledge about the use cases and their side effects by yourself without
the systematic control of the full OSLiC process as presented here.}:

\tikzstyle{decision} = [diamond, draw, fill=gray!20, 
    text width=4.5em, text badly centered, node distance=4cm, inner sep=0pt]

\tikzstyle{preparation} = [rectangle, draw, fill=gray!30, 
    text width=10em, text centered, rounded corners, minimum height=4em]
 
\tikzstyle{lprocs} = [rectangle, draw, fill=gray!40, 
    text width=10em, text centered, rounded corners, minimum height=4em]
    
\tikzstyle{processing} = [rectangle, draw, fill=gray!40, node distance=2.4cm,
    text width=15em, text centered, rounded corners, minimum height=4em]
    
\tikzstyle{line} = [draw, -latex']

\tikzstyle{cloud} = [draw, ellipse, text width=6em, text centered, fill=gray!10]
 
    
\begin{tikzpicture}[node distance =1.9cm, auto]
\footnotesize
    % Place nodes
    
  \node [cloud] (start) at (1,10) 
    {$\forall$  \\ Open Source \\ components};
  \node [preparation] (select) at (5,10) 
    {select next Open Source component};     
  \node [preparation,  below of=select] (analyze) 
    {analyze its role in software architecture and 
    determine general use of app};  
  \node [preparation,  below of=analyze] (determine) 
    {determine Open Source License};
  \node [lprocs,  below of=determine] (fillin)
    {\textbf{fill in the 5 query form} ($\rightarrow$ p.
    \pageref{OSLiCStandardFormForGatheringInformation})};
    
  \node [decision, right of=fillin] (success) {success?};
  
  \node [processing,  below of=success] (traverse)
    {\textbf{traverse the} taxonomic \textbf{Open Source Use Case Finder}
    ($\rightarrow$ \pageref{OSLiCUseCaseFinder}) and jump to the indicated
    \textbf{O}pen \textbf{S}ource \textbf{U}se \textbf{C}ase page ($\rightarrow$
    \pageref{OSUCList}ff.)};
    
  \node [processing,  below of=traverse] (find)
    {\textbf{Determine} page of \textbf{license and use case specific to-do list}
    presented in license specific chapter};
 
  \node [processing,  below of=find] (process)
    {Jump to indicated page and \textbf{process license and use case specific
    to-do list} ($\rightarrow$ \pageref{OSUCToDoLists}ff.)};
    
  \node [decision, right of=process] (other) {more?};
  \node [cloud, below of=other] (stop) {stop};

  \path [line] (start) -- (select);  
     
  \path [line] (select) -- (analyze);      
  \path [line] (analyze) -- (determine);         
  \path [line] (determine) -- (fillin);
  \path [line] (fillin) -- (success);
  
  \path [line] (success) |- node [near start] {no} (analyze);
  \path [line] (success) -- node [near start] {yes} (traverse);             
  
  \path [line] (traverse) -- (find);              
  \path [line] (find) -- (process);
  \path [line] (process) -- (other);

  \path [line] (other) |- node [near start] {yes} (select);
  \path [line] (other) -- node [near start] {no} (stop);                      

\end{tikzpicture}

Second, the readers might wish to comprehend the whole analysis. So, we
shortly discuss Open Source License taxonomies as the basis for license compliant
behavior\footnote{$\rightarrow$ \enquote{\nameref{sec:LicenseTaxonomies}}, pp.
\pageref{sec:LicenseTaxonomies}}. We consider some side effects with
regard to Open Source License compliance\footnote{$\rightarrow$
\enquote{\nameref{sec:SideEffects}}, pp. \pageref{sec:SideEffects}}. And we
study the structure of Open Source Use Cases\footnote{$\rightarrow$
\enquote{\nameref{sec:OSUCdeduction}}, pp. \pageref{sec:OSUCdeduction}}.

So, let's close our introduction by using, modifying, and (re)distributing a well
known wish of a well known man: Happy (Legally) Hacking.

%\bibliography{../../../bibfiles/oscResourcesEn}
