% Telekom osCompendium 'for beeing included' snippet template
%
% (c) Karsten Reincke, Deutsche Telekom AG, Darmstadt 2011
%
% This LaTeX-File is licensed under the Creative Commons Attribution-ShareAlike
% 3.0 Germany License (http://creativecommons.org/licenses/by-sa/3.0/de/): Feel
% free 'to share (to copy, distribute and transmit)' or 'to remix (to adapt)'
% it, if you '... distribute the resulting work under the same or similar
% license to this one' and if you respect how 'you must attribute the work in
% the manner specified by the author ...':
%
% In an internet based reuse please link the reused parts to www.telekom.com and
% mention the original authors and Deutsche Telekom AG in a suitable manner. In
% a paper-like reuse please insert a short hint to www.telekom.com and to the
% original authors and Deutsche Telekom AG into your preface. For normal
% quotations please use the scientific standard to cite.
%
% [ File structure derived from 'mind your Scholar Research Framework' 
%   mycsrf (c) K. Reincke CC BY 3.0  http://mycsrf.fodina.de/ ]

%

%%% \chapter*{Disclaimer} %%%

This book shall be thoroughly developed---together with the open source
community. At the end it shall deliver reliable information. But nevertheless,
the \oslic{} can not offer more than the opinion(s) of its authors and
contributors. It is only one voice of the chorus discussing the open source
licenses. For protecting the authors and contributors from charges and claims of
indemnification we adopt the lightly modified GPL3 disclaimer:

{
\newcommand\gummi{\hspace{0pt plus 1pc}}
THERE IS NO WARRANTY FOR THE \oslic{}, TO THE EXTENT PERMITTED BY APPLICABLE LAW.
THE COPYRIGHT HOLDERS AND/OR OTHER PARTIES PROVIDE THE TEXT “AS IS” WITHOUT
WARRANTY OF ANY KIND, EITHER EXPRESSED OR IMPLIED, INCLUDING, BUT NOT LIMITED
TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR
PURPOSE. THE ENTIRE RISK AS TO THE QUALITY AND PERFORMANCE OF THE \oslic{} IS
WITH YOU. \gummi SHOULD THE \oslic{} PROVE DEFECTIVE, \gummi YOU ASSUME THE COST OF ALL
NECESSARY SERVICING, REPAIR OR CORRECTION.

IN NO EVENT \gummi UNLESS REQUIRED BY APPLICABLE LAW \gummi OR AGREED TO IN WRITING WILL ANY
COPYRIGHT HOLDER, OR ANY OTHER PARTY WHO MODIFIES AND/OR CONVEYS THE \oslic{} AS
PERMITTED ABOVE, BE LIABLE TO YOU FOR DAMAGES, INCLUDING ANY GENERAL, \gummi SPECIAL, \gummi
INCIDENTAL \gummi OR CONSEQUENTIAL DAMAGES ARISING OUT OF THE USE OR INABILITY TO USE
THE \oslic{} (INCLUDING BUT NOT LIMITED TO LOSS OF DATA OR DATA BEING RENDERED
INACCURATE OR LOSSES SUSTAINED BY YOU OR THIRD PARTIES OR A FAILURE OF THE
\oslic{} TO COOPERATE WITH ANY OTHER TOOLS), EVEN IF SUCH HOLDER OR OTHER PARTY
HAS BEEN ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.
}

\textit{Particularly, it must be highlighted that - referred to your solitary
case - the \oslic{} can not and shall not replace a legal review or a legal advice
by lawyers. The \oslic{} is only dealing with prototypic use cases. So, it may
inspire developers, managers, open source experts, and companies to find good
solutions which they finally should let be reviewed by legal
counselors.}\footnote{For German readers: The \oslic{} naturally respects the German
'Rechtsdienstleistungsgesetz'. It only contains legal reflections addressed to a
general public. The \oslic{} may only be read as an \enquote{nur an die
Allgemeinheit gerichtete Darstellung und Erörterung von Rechtsfragen.}}

% Local Variables:
% mode: latex
% fill-column: 80
% End:
